---
title: "p8106_stl2137_hw5"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ISLR)
library(caret)
library(e1071)
```

```{r}
data("OJ")
dat_oj <- OJ %>% 
  janitor::clean_names()

set.seed(1)

rowTrain <- createDataPartition(y = dat_oj$purchase,
                               p = 799/1070,
                               list = FALSE)
```

## Part A
What are the training and test error rates?

### Linear Training Data Performance

```{r}
control1 <- trainControl(method = "cv")

set.seed(1)
svm_linear_fit <- train(purchase ~ ., 
                  data = dat_oj[rowTrain,], 
                  method = "svmLinear2",
                  preProcess = c("center", "scale"),
                  tuneGrid = data.frame(cost = exp(seq(-1,4,len=20))),
                  trControl = control1)

ggplot(svm_linear_fit, highlight = TRUE)
```

The training error rate for the linear kernel support vector classifier is `r 1 - max(svm_linear_fit$results$Accuracy)`. 

### Linear Test Data Performance

```{r}
pred_svm_linear <- predict(svm_linear_fit, newdata = dat_oj[-rowTrain,])


confusion_matrix_svm_linear <- confusionMatrix(data = pred_svm_linear, 
                reference = dat_oj$purchase[-rowTrain])
```

The test error rate for the linear kernel support vector classifier is `r 1 - confusion_matrix_svm_linear$overall[1]`. 

## Part B
What are the training and test error rates?
```{r}
svm_radial_grid <- expand.grid(C = exp(seq(0,5,len=10)),
                         sigma = exp(seq(-5,-5,len=5)))
set.seed(1)             
svm_radial_fit <- train(purchase ~ ., dat_oj, 
                  subset = rowTrain,
                  method = "svmRadial",
                  preProcess = c("center", "scale"),
                  tuneGrid = svm_radial_grid,
                  trControl = control1)

ggplot(svm_radial_fit, highlight = TRUE)
```

The training error rate for the support vector machine with a radial kernel is `r 1 - max(svm_radial_fit$results$Accuracy)`.

### Radial Test Data Performance

```{r}
pred_svm_radial <- predict(svm_radial_fit, newdata = dat_oj[-rowTrain,])


confusion_matrix_svm_radial <- confusionMatrix(data = pred_svm_radial, 
                reference = dat_oj$purchase[-rowTrain])
```

The test error rate for the support vector machine with a radial kernel is `r 1 - confusion_matrix_svm_radial$overall[1]`. 
